Learning Constraints and Optimization Criteria

### 2015-12-14 Paper.tex
Working to incorporate changes

@@

Learning constraints has been addressed in constraint programming (e.g. \cite{Beldiceanu:ModelSeeker,bessiere2013constraint}) and inductive logic programming (e.g. \cite{DeRaedt:ClausalDiscovery}).
Recent efforts \cite{Lallouet:LearningCP} have attempted to combine these two fields.
Furthermore, \cite{campigotto2011active} have learned propositional weighted MAX-SAT theories from examples.

We use weighted first-order logical theories to represent constraint optimization problems.
The weights capture the optimization function, and (first-order) weighted MAX-SAT can be used to determine the \emph{best} solutions.
Furthermore, we learn such models by combining inductive logic programming (ILP) principles (such as clausal discovery \cite{DeRaedt:ClausalDiscovery}) with preference learning.
We use ILP to learn the clausal theories from interpretations, and preference learning to determine the weights.
Therefore, users provide examples of possible worlds and a set of preferences that specify which examples are preferred over other ones.
This setting extends traditional constraint learning and ILP approaches with the ability to learn soft constraints and integrates constraint satisfaction and optimization.
It also extends the approach of \cite{campigotto2011active} as first-order theories are learned and preferences are used rather than examples with target values.

@@

@@

\paragraph{Future work}
There are several opportunities for future work.
It would be interesting to adapt the number of variables and literals per clause dynamically, as they have a strong influence on the efficiency and accuracy of the clause learning system.
Additionally, interactivity could be added to the learning system by actively generating examples or preferences and querying the user about their validity.

@@

\section*{Acknowledgments}
The author thanks his promoters Luc De Raedt and Anton Dries.
Samuel Kolb is supported by the Research Foundation - Flanders (FWO).

\newpage
%
% ---- Bibliography ----
%
\bibliography{Bibliography}
\bibliographystyle{aaai}
\end{document}

>>>>

\begin{itemize}
  \item \sam{Why interesting, connection to Campignotto, Domingos, Kok, Why preferences useful?}
  \item \sam{Real tasks with preferences? Small scale evaluation}
  \item \sam{Lot of background knowledge assumed (vs. constraint programming, probabilistic programming, demo model and need for learning)}
\end{itemize}

@@

Constraint learning is the task of discovering constraints from data.
This task has been addressed in constraint programming (e.g. \cite{Beldiceanu:ModelSeeker,bessiere2013constraint}) and inductive logic programming (e.g. \cite{DeRaedt:ClausalDiscovery}).
Recent efforts \cite{Lallouet:LearningCP} have attempted to combine these two fields.
Furthermore, \cite{campigotto2011active} have learned propositional weighted MAX-SAT theories from examples.

We use weighted first-order logical theories to represent constrained optimization problems.
The weights capture the optimization function, and (first-order) weighted MAX-SAT can be used to determine the \emph{best} solutions.
Furthermore, we learn such models by combining inductive logic programming (ILP) principles (such as clausal discovery \cite{DeRaedt:ClausalDiscovery}) with preference learning.
We use ILP to learn the clausal theories from interpretations, and preference learning to determine the weights.
Therefore, users provide examples of possible worlds and a set of preferences that specify which examples are preferred over other ones.
This setting extends traditional constraint learning and ILP approaches with the ability to learn soft constraints and integrates constraint satisfaction and optimization.
It also extends the propositional approach of \cite{campigotto2011active} as first-order theories are learned and preferences are used rather than examples with target values.
Preferences are useful in situation where the score of an example is hard to quantify and in interactive settings because it is often easier for humans to provide preferences over few examples at a time than absolute scores.

@@

% We use preferences for learning as it is often easier for humans to provide preferences over few examples at a time than absolute scores.
% This makes them useful in interactive settings and in situations where an examples absolute score is hard to quantify.

% One of the main advantages of using preferences for learning is that preferences are often easier to provide for humans and only consider few examples at a time.
% Consequently, they are useful in interactive settings and in situations where an examples absolute score is hard to quantify.

@@

\paragraph{Future work}
There are several opportunities for future work.
In the current approach weight learning is performed using preferences and a learn-to-rank SVM.
It would, however, be easy to use another type of input (e.g. absolute scores) and a corresponding SVM.

It would be interesting to adapt the number of variables and literals per clause dynamically, as they have a strong influence on the efficiency and accuracy of the clause learning system.
Additionally, interactivity could be added to the learning system by actively generating examples or preferences and querying the user about their validity.

@@

\section*{Acknowledgments}
The author thanks his promoters Luc De Raedt and Anton Dries.
Furthermore, he is is thankful for the help provided by Bart Bogaerts, Jesse Davis, Marc Denecker, Vladimir Dzyuba, Angelika Kimmig and Jan Tobias M\"uhlberg.
Samuel Kolb is supported by the Research Foundation - Flanders (FWO).

\newpage

% -------------------------------------------------
% Bibliography
% -------------------------------------------------

\bibliography{Bibliography}
\bibliographystyle{aaai}
\end{document}
